\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Simplify DLT descriptions

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data. Therefore, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

>>>>

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amounts of data emerges, several researchers have started to explore the design of the data marketplace. The Third Party Auditors (TPAs)-based framework\cite{TPA} is far from being satisfactory due to the unstandardized data format and dynamic nature of IoT data. Thus, a decentralized data integrity validation and trading process has been proposed in recent years, and distributed ledger technology (DLT) is considered that the existence of data can be trusted and no longer rely on any third party authority.
